---
title: "Figure 1"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, output_dir = "C:/Projects/ForecastEvaluation/HTML", encoding = encoding) })
urlcolor: blue
linkcolor: red
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6, fig.align = "left", warning=FALSE, echo=TRUE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

------------------------------------------------------------------------
```{r libraries, results='hide', warning=FALSE, message=FALSE, echo = FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(patchwork)
library(kableExtra)
library(viridis)
library(scico)

library(scoringutils)
library(hubUtils)
library(hubEnsembles)
library(hubData)
```

# Data
```{r}
state_coverage <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_coverage.csv")
# state_coverage_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_coverage_summary.csv")
state_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis.csv")
# state_wis_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis_summary.csv")

standard_coverage <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_coverage.csv")
# standard_coverage_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_coverage_summary.csv")
standard_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis.csv")
# standard_wis_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis_summary.csv")
```

# Subfigures
```{r}
model_ids <- c("NAU-Copycat", "NAU-INFLAenza", "UMass-SAR", "UMass-alloy", "UT-GBQR", "VTSanghani-PRIME", "epiENGAGE-baseline", "epiENGAGE-ensemble_mean", "epiENGAGE-lop_norm", "epiforecasts-dyngam")
```

## Figure 1a
```{r}
temp1a_state = state_wis |> group_by(model_id, target) |>  summarise(mean_wis = mean(wis), count = n(), .groups = 'drop')
temp1a_state$type = "state-scoring"

temp1a_standard = standard_wis |> group_by(model_id, target) |>  summarise(mean_wis = mean(wis), count = n(), .groups = 'drop')
temp1a_standard$type = "standard-scoring"

temp1a = rbind(temp1a_standard, temp1a_state)
temp1a = temp1a |> 
  filter(target == "Flu ED visits pct",
         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble")

temp1a$model_id <- factor(temp1a$model_id,
  levels = model_ids)
```

```{r}
knitr::kable(temp1a)
```

```{r}
figure1a = ggplot(temp1a, aes(x = model_id, y = mean_wis, fill = type)) + 
  geom_col(position = "dodge", color = "black") + 
  scale_fill_manual(values = c("standard-scoring" = "firebrick", "state-scoring" = "royalblue")) +
  scale_y_continuous(expand = expansion(mult = 0, add = 0.03)) +
  labs(x = "Model", y = "Mean WIS", fill = "Scoring Method") + 
  theme_bw() + theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) +
  theme(legend.position = "top") + scale_x_discrete(labels = function(x) gsub("-", "-\n", x))

figure1a
```

### Location version 
```{r}
temp1a_state = state_wis |> filter(target == "Flu ED visits pct") |> filter(model_id != "epiENGAGE-GBQR") |> filter(model_id != "FluSight-ensemble") |> group_by(location, target) |>  summarise(mean_wis = mean(wis), count = n(), .groups = 'drop')
temp1a_state$type = "state-scoring"

temp1a_standard = standard_wis |> filter(target == "Flu ED visits pct") |> filter(model_id != "epiENGAGE-GBQR") |> filter(model_id != "FluSight-ensemble") |> group_by(location, target) |>  summarise(mean_wis = mean(wis), count = n(), .groups = 'drop')
temp1a_standard$type = "standard-scoring"

temp1a = rbind(temp1a_standard, temp1a_state)
```

```{r}
knitr::kable(temp1a)
```

```{r, fig.height = 10, fig.width = 10}
figure1a_loc = ggplot(temp1a, aes(x = location, y = mean_wis, fill = type)) + 
  geom_col(position = "dodge", color = "black") + 
  scale_fill_manual(values = c("standard-scoring" = "firebrick", "state-scoring" = "royalblue")) +
  scale_y_continuous(limits = c(0, 2.5), breaks = c(0.5, 1, 1.5, 2, 2.5, 3),
                     expand = expansion(mult = 0, add = 0.03)) +
  labs(x = "Model", y = "Mean WIS", fill = "Scoring Method") + 
  theme_bw() + theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) +
  theme(legend.position = "top") 

figure1a_loc
```

## Figure 5
```{r}
state_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis.csv")
standard_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis.csv")
state_wis = state_wis |> rename(state_wis = wis)

complete_wis <- state_wis %>%
  left_join(standard_wis, by = intersect(colnames(state_wis), colnames(standard_wis)))

# complete_wis$relative_wis <- complete_wis$wis / complete_wis$state_wis
complete_wis = complete_wis |> select("location", "target_end_date", "horizon", "reference_date",  "model_id", "target", "wis",  "state_wis") |> filter(         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble")

# complete_wis <- complete_wis %>%
#   filter(wis > 0)
```

```{r}
sum(is.na(complete_wis)) 
# complete_wis = na.omit(complete_wis)
```

```{r}
complete_wis_long <- complete_wis %>%
  pivot_longer(
    cols = c("wis", "state_wis"),
    names_to = "method",
    values_to = "wis_score"
  ) %>%
  mutate(method = case_when(
    method == "wis" ~ "standard",
    method == "state_wis" ~ "state"
  ))

complete_wis_long <- complete_wis_long %>% rename(wis = wis_score)

class(complete_wis_long) <- c("scores", "data.table", class(complete_wis_long))
attr(complete_wis_long, "metrics") <- "wis"

head(complete_wis_long)
```
### Version 1
```{r}
temp1b <- suppressWarnings(
  complete_wis_long %>%
    filter(target == "Flu ED visits pct") %>%
    get_pairwise_comparisons(
      compare = "method",
      by = c("model_id", "location"),
      baseline = "state"
    ) %>%
    filter(
      method == "standard",
      compare_against == "state",
      !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
      model_id != "FluSight-ensemble"
    ) %>%
    mutate(model_id = factor(model_id, levels = model_ids))
)
```

```{r}
#knitr::kable(temp1b)
```

```{r, fig.height = 10, fig.width = 10}
figure1b_loc <- ggplot(temp1b, aes(x = model_id, y = location, fill = log(wis_scaled_relative_skill))) + 
  scale_fill_gradient2(
  low = "#2166ac", 
  mid = "grey90", 
  high = "#d73027", 
  midpoint = 0
) + 
  geom_tile(col = "black") + 
  labs(x = "Model", y = "Location", fill = "Scaled Relative Skill Score (WIS)") + 
  theme_bw() + 
  theme(
    legend.position = "top",
    text = element_text(size = 14),
    axis.text.x = element_text(size = 11, angle = 30, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 13),
    strip.text = element_text(size = 12)  
  ) + scale_x_discrete(labels = function(x) gsub("-", "-\n", x))

figure1b_loc
```

### Version 2
```{r}
temp1b_date <- suppressWarnings(
  complete_wis_long %>%
    filter(target == "Flu ED visits pct") %>%
    get_pairwise_comparisons(
      compare = "method",
      by = c("model_id", "target_end_date"),
      baseline = "state"
    ) %>%
    filter(
      method == "standard",
      compare_against == "state",
      !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
      model_id != "FluSight-ensemble"
    ) %>%
    mutate(model_id = factor(model_id, levels = model_ids))
)
```

```{r, fig.height = 10, fig.width = 10}
figure1b_date <- ggplot(temp1b_date, aes(x = model_id, y = target_end_date, fill = log(wis_scaled_relative_skill))) + 
  scale_fill_gradient2(
  low = "#2166ac", 
  mid = "grey90", 
  high = "#d73027", 
  midpoint = 0
) +  
  geom_tile(col = "black") +
  labs(x = "Model", y = "Date", fill = "Scaled Relative Skill Score (WIS)") + 
  theme_bw() + 
  theme(
    legend.position = "top",
    text = element_text(size = 14),
    axis.text.x = element_text(size = 11, angle = 30, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 13),
    strip.text = element_text(size = 12)  
  ) + scale_x_discrete(labels = function(x) gsub("-", "-\n", x))
figure1b_date
```

### Date line
```{r}
temp1b_date_line <- suppressWarnings(
  complete_wis_long %>%
    filter(target == "Flu ED visits pct") %>%
    get_pairwise_comparisons(
      compare = "method",
      by = c("model_id", "target_end_date", "horizon"),
      baseline = "state"
    ) %>%
    filter(
      method == "standard",
      compare_against == "state",
      !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
      model_id != "FluSight-ensemble"
    ) %>%
    mutate(model_id = factor(model_id, levels = model_ids))
)
```

```{r}
horizon_labels <- c(
  "1" = "Horizon 1",
  "2" = "Horizon 2",
  "3" = "Horizon 3",
  "4" = "Horizon 4"
)
```

```{r}
figure1b_date_line <- ggplot(temp1b_date_line, aes(x = as.Date(target_end_date), y = wis_scaled_relative_skill, color = model_id)) + 
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1,linetype = "dashed", color = "black") +
  scale_y_log10() +
  scale_color_manual(
    values = c(setNames(scales::hue_pal()(length(unique(temp1b_date_line$model_id)) - 1),
                         setdiff(unique(temp1b_date_line$model_id), "epiENGAGE-ensemble_mean")),
                "epiENGAGE-ensemble_mean" = "black")
  ) +
  labs(x = "Date", y = "Scaled Relative Skill Score") + 
  theme_bw() + 
  theme(
    legend.position = "top",
    text = element_text(size = 14),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 13)
  ) + 
  scale_x_date(
  date_breaks = "1 month",
  date_labels = "%b %Y"
) + facet_wrap(~horizon, ncol = 2, labeller = as_labeller(horizon_labels))
figure1b_date_line
```

## Figure 1c (SRSS)
```{r}
state_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis.csv")
standard_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis.csv")
state_wis = state_wis |> rename(state_wis = wis)

complete_wis <- state_wis %>%
  left_join(standard_wis, by = intersect(colnames(state_wis), colnames(standard_wis)))

# complete_wis$relative_wis <- complete_wis$wis / complete_wis$state_wis
complete_wis = complete_wis |> select("location", "target_end_date", "horizon", "reference_date",  "model_id", "target", "wis",  "state_wis") |> filter(         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble")

# complete_wis <- complete_wis %>%
#   filter(wis > 0)
```

```{r}
sum(is.na(complete_wis)) 
# complete_wis = na.omit(complete_wis)
```

```{r}
complete_wis_long <- complete_wis %>%
  pivot_longer(
    cols = c("wis", "state_wis"),
    names_to = "method",
    values_to = "wis_score"
  ) %>%
  mutate(method = case_when(
    method == "wis" ~ "standard",
    method == "state_wis" ~ "state"
  ))

complete_wis_long <- complete_wis_long %>% rename(wis = wis_score)

class(complete_wis_long) <- c("scores", "data.table", class(complete_wis_long))
attr(complete_wis_long, "metrics") <- "wis"

head(complete_wis_long)
```

```{r}
comparisons_by_model <- get_pairwise_comparisons(
  scores = complete_wis_long,
  compare = "method",
  by = "model_id",
  baseline = "state"
)

head(comparisons_by_model)

comparisons_by_location <- get_pairwise_comparisons(
  scores = complete_wis_long,
  compare = "method",
  by = "location",
  baseline = "state"
)

head(comparisons_by_location)
```

```{r}
temp1c_model <- comparisons_by_model %>%
  filter(method == "standard", compare_against == "state")

temp1c_model$model_id <- factor(temp1c_model$model_id,
  levels = model_ids)

knitr::kable(temp1c_model)

temp1c_loc <- comparisons_by_location %>%
  filter(method == "standard", compare_against == "state")

lookup = read.csv("data/lookup.csv")
temp1c_loc = temp1c_loc |> left_join(lookup, by = "location") 
temp1c_loc = temp1c_loc |>
  arrange(desc(state), wis_scaled_relative_skill) |>
  mutate(location = factor(location, levels = location))

knitr::kable(temp1c_loc)
```

```{r}
figure1c_model = ggplot(temp1c_model, aes(x = model_id, y = wis_scaled_relative_skill)) + 
  geom_col(fill = "firebrick", color = "black") + 
  labs(x = "Model", y = "Scaled relative skill score (WIS)") + 
   theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) + scale_y_log10() + scale_x_discrete(labels = function(x) gsub("-", "-\n", x)) + 
  theme(legend.position = "top") + geom_hline(aes(yintercept = 1), col = "black", linetype = "dashed", linewidth = 1.2)

figure1c_model
```

```{r, fig.height=6, fig.width=14}
state_boundaries = which(diff(as.numeric(factor(temp1c_loc$state))) != 0) + 0.5

figure1c_loc = ggplot(temp1c_loc, aes(x = location, y = wis_scaled_relative_skill, fill = state)) + 
  geom_col(color = "black") + 
  labs(x = "Location", y = "Scaled relative skill score (WIS)") + 
  theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 50, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) +
  theme(legend.position = "top") + scale_y_log10() + 
  geom_hline(aes(yintercept = 1), col = "black", linetype = "dashed", linewidth = 1.2) +
  geom_vline(xintercept = state_boundaries, color = "black", linewidth = 1.0)

figure1c_loc
```

## Figure 6
### Local
```{r}
raw = read.csv("Data/raw_data.csv")
```

```{r}
set_horizon = 3
```

```{r, fig.width=10, fig.height=10}
plot_data <- raw %>%
  filter(output_type == "quantile") %>%
  mutate(
    output_type_id = as.numeric(output_type_id),
    date = as.Date(target_end_date)
  ) %>%
  pivot_wider(
    names_from = output_type_id,
    values_from = value,
    names_prefix = "q_"
  ) %>%
  rename(
    observed = oracle_value,
    predicted_value = `q_0.5`,  
    lower = `q_0.025`,           
    upper = `q_0.975`            
  ) |> filter(model_id == "epiENGAGE-ensemble_mean") |> filter(horizon == set_horizon) |> 
  filter(location %in% c("austin", "san-antonio",  "el-paso", "indianapolis", "pittsfield", "portland")) 

plot_data$location = factor(plot_data$location, levels = c("austin", "san-antonio",  "el-paso", "indianapolis", "pittsfield", "portland"))
```

```{r, fig.width=20, fig.height=10}
obsvspred_loc <- ggplot(plot_data, aes(x = date)) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = "Prediction Interval"),
              alpha = 0.4, color = NA) +
  geom_line(aes(y = predicted_value, color = "Predicted HSA"),
            linewidth = 1) +
  geom_point(aes(y = observed, color = "Observed HSA"),
             size = 2, shape = 16) +
  facet_wrap(~location, nrow=1) +
  scale_color_manual(
    name = NULL,
    values = c(
      "Observed HSA" = "#E74C3C",
      "Predicted HSA" = "#F39C12"
    )
  ) +
  scale_fill_manual(
    name = NULL,
    values = c("Prediction Interval" = "#F39C12")
  ) +
  labs(
    x = NULL,
    y = "Percent Influenza ED Visits"
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    legend.position = "bottom",
    strip.text = element_text(size = 17)  
  ) + scale_x_date(date_breaks = "2 months", date_labels = "%b") 
```

### State
```{r}
raw_state = read.csv("Data/state_raw.csv")
```

```{r, fig.width=10, fig.height=10}
plot_data_state <- raw_state %>%
  filter(output_type == "quantile") %>%
  mutate(
    output_type_id = as.numeric(output_type_id),
    date = as.Date(target_end_date)
  ) %>%
  pivot_wider(
    names_from = output_type_id,
    values_from = state_value,
    names_prefix = "q_"
  ) %>%
  rename(
    observed = oracle_value,
    predicted_value = `q_0.5`,  
    lower = `q_0.025`,           
    upper = `q_0.975`            
  ) |> filter(model_id == "epiENGAGE-ensemble_mean") |> filter(horizon == set_horizon) |> 
  filter(location %in% c("austin", "san-antonio",  "el-paso", "indianapolis", "pittsfield", "portland")) 

plot_data_state$location = factor(plot_data_state$location, levels = c("austin", "san-antonio",  "el-paso", "indianapolis", "pittsfield", "portland"))
```

```{r, fig.width=20, fig.height=10}
obsvspred_state <- ggplot(plot_data_state, aes(x = date)) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = "Prediction Interval"),
              alpha = 0.4, color = NA) +
  geom_line(aes(y = predicted_value, color = "Predicted HSA"),
            linewidth = 1) +
  geom_point(aes(y = observed, color = "Observed HSA"),
             size = 2, shape = 16) +
  facet_wrap(~location, nrow=1) +
  scale_color_manual(
    name = NULL,
    values = c(
      "Observed HSA" = "#E74C3C",
      "Predicted HSA" = "black"
    )
  ) +
  scale_fill_manual(
    name = NULL,
    values = c("Prediction Interval" = "darkgray")
  ) +
  labs(
    x = NULL,
    y = "Percent Influenza ED Visits"
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    legend.position = "bottom",
    strip.text = element_text(size = 17)  
  ) + scale_x_date(date_breaks = "2 months", date_labels = "%b") 
```

```{r, fig.width=20, fig.height=15}
fig1c_timeseries = obsvspred_loc / obsvspred_state
fig1c_timeseries
```


## Figure 1d
```{r}
temp1d_state = state_coverage |> group_by(model_id, target) |>  
  summarise(mean_coverage = mean(coverage_95), count = n(), .groups = 'drop')
temp1d_state$type = "state-scoring"

temp1d_standard = standard_coverage |> group_by(model_id, target) |> 
  summarise(mean_coverage = mean(coverage_95), count = n(), .groups = 'drop')
temp1d_standard$type = "standard-scoring"

temp1d = rbind(temp1d_standard, temp1d_state)
temp1d = temp1d |> filter(target == "Flu ED visits pct",
         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble") 

temp1d$model_id <- factor(temp1d$model_id,
  levels = model_ids)
```

```{r}
knitr::kable(temp1d)
```

```{r}
figure1d = ggplot(temp1d, aes(x = model_id, y = mean_coverage, fill = type)) + 
  geom_col(col = "black", position = "dodge") + 
  scale_fill_manual(values = c("standard-scoring" = "firebrick", "state-scoring" = "royalblue")) +
  labs(x = "Model", y = "Mean Coverage (95%)", fill = "Scoring Method") + 
  theme_bw() + 
  theme(legend.position = "top") + 
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) + scale_y_continuous(expand = expansion(mult = 0, add = 0.03)) + scale_x_discrete(labels = function(x) gsub("-", "-\n", x)) + geom_hline(yintercept = 0.95, linetype = "dashed",linewidth = 1)



figure1d
```

```{r, fig.height = 10, fig.width = 10}
temp1d_state = state_coverage |> group_by(model_id, target, horizon) |>  
  summarise(mean_coverage = mean(coverage_95), count = n(), .groups = 'drop')
temp1d_state$type = "state-scoring"

temp1d_standard = standard_coverage |> group_by(model_id, target, horizon) |> 
  summarise(mean_coverage = mean(coverage_95), count = n(), .groups = 'drop')
temp1d_standard$type = "standard-scoring"

temp1d = rbind(temp1d_standard, temp1d_state)
temp1d = temp1d |> filter(target == "Flu ED visits pct",
         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble") 

temp1d$model_id <- factor(temp1d$model_id,
  levels = model_ids)

figure1d_split = ggplot(temp1d, aes(x = model_id, y = mean_coverage, fill = type)) + 
  geom_col(col = "black", position = "dodge") + 
  scale_fill_manual(values = c("standard-scoring" = "firebrick", "state-scoring" = "royalblue")) +
  labs(x = "Model", y = "Mean Coverage (95%)", fill = "Scoring Method") + 
  theme_bw() + 
  theme(legend.position = "top") + 
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) + scale_y_continuous(expand = expansion(mult = 0, add = 0.03)) + 
  scale_x_discrete(labels = function(x) gsub("-", "-\n", x)) + geom_hline(yintercept = 0.95, linetype = "dashed",linewidth = 1) + facet_wrap(~horizon,labeller = labeller(horizon = as_labeller(function(x) paste("Horizon", as.numeric(x) + 1))))

figure1d_split
```


## Extra
### 50% coverage rate
```{r}
standard_coverage_50 = read.csv("Data/standard-scoring/standard_coverage_50.csv")
state_coverage_50 = read.csv("Data/state-scoring/state_coverage_50.csv")

temp50_stat = state_coverage_50 |> group_by(model_id, target, horizon) |>  
  summarise(mean_coverage = mean(coverage_50), count = n(), .groups = 'drop')
temp50_stat$type = "state-scoring"

temp50_stan = standard_coverage_50 |> group_by(model_id, target, horizon) |> 
  summarise(mean_coverage = mean(coverage_50), count = n(), .groups = 'drop')
temp50_stan$type = "standard-scoring"

temp50 = rbind(temp50_stan, temp50_stat)
temp50 = temp50 |> filter(target == "Flu ED visits pct",
         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble") 

temp50$model_id <- factor(temp50$model_id,
  levels = model_ids)
```

```{r}
knitr::kable(temp50)
```

```{r, fig.height = 10, fig.width = 10}
figure_50_split = ggplot(temp50, aes(x = model_id, y = mean_coverage, fill = type)) + 
  geom_col(col = "black", position = "dodge") + 
  scale_fill_manual(values = c("standard-scoring" = "firebrick", "state-scoring" = "royalblue")) +
  labs(x = "Model", y = "Mean Coverage (50%)", fill = "Scoring Method") + 
  theme_bw() + 
  theme(legend.position = "top") + 
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) + scale_y_continuous(expand = expansion(mult = 0, add = 0.03)) + scale_x_discrete(labels = function(x) gsub("-", "-\n", x)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed",linewidth = 1) + facet_wrap(~horizon,  labeller = labeller(horizon = as_labeller(function(x) paste("Horizon", as.numeric(x) + 1))))

figure_50_split
```


### Combined location model rWIS plot
```{r}
state_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis.csv")
standard_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis.csv")
state_wis = state_wis |> rename(state_wis = wis)
```

```{r}
complete_wis <- state_wis %>%
  left_join(standard_wis, by = intersect(colnames(state_wis), colnames(standard_wis)))

complete_wis$relative_wis <- complete_wis$wis / complete_wis$state_wis
complete_wis = complete_wis |> select("location", "target_end_date", "horizon", "reference_date",  "model_id", "target", "wis",  "state_wis",    "relative_wis")

complete_wis <- complete_wis %>%
  filter(wis > 0)
```

```{r}
complete_wis_summary <- complete_wis %>%
  group_by(model_id, location) %>%
  summarise(
    mean_relative_wis = mean(relative_wis[!is.infinite(relative_wis)]),
    count = n(),
    .groups = 'drop'
  )

temp_special = complete_wis_summary |> filter(         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble") 

temp_special$model_id <- factor(temp_special$model_id,
  levels = model_ids)

lookup = read.csv("Data/lookup.csv")
temp_special = temp_special |> left_join(lookup, by = "location")
```

he rWIS figure with location on the x-axis, rWIS on the y-axis, displayed as a dot plot with points colored by model.
Since this is rWIS, the y-axis should be on a log scale centered at 1, so that values such as rWIS = 0.5 and rWIS = 2 are equidistant from 1.
```{r, fig.height=20, fig.width=20}
state_order = temp_special |>
  distinct(location, state) |>
  arrange(state, location)

state_boundaries = which(diff(as.numeric(factor(state_order$state))) != 0) + 0.5

ggplot(temp_special) + geom_point(size=5, aes(x=location, y=mean_relative_wis, color = as.factor(model_id)))+ 
  labs(y = "Effect (rWIS)", x = "Model") + 
  theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 16, angle = 50, hjust = 1, vjust = 1),
    axis.text.y = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 17),
    strip.text = element_text(size = 17)  
  ) +
  theme(legend.position = "top") +
  scale_y_log10() +
  geom_hline(aes(yintercept = 1), col = "black", linetype = "dashed", linewidth = 1.2) + geom_vline(xintercept = state_boundaries, color = "black", linewidth = 1.0)
```

### NA stuff
```{r}
sum(is.na(complete_wis$wis))
na <- complete_wis %>%
  filter(if_any(everything(), is.na))

table(na$location)
table(na$target_end_date)
table(na$model_id)
```

```{r}
# complete_wis = na.omit(complete_wis)
standard_wis$horizon = as.character(standard_wis$horizon)

complete_wis$model_id <- droplevels(as.factor(complete_wis$model_id))
complete_wis$horizon <- droplevels(as.factor(complete_wis$horizon))
complete_wis$location <- droplevels(as.factor(complete_wis$location))

complete_wis = complete_wis |> filter(target == "Flu ED visits pct",
         !model_id %in% c("epiENGAGE-GBQR", "ACCIDDA-InfluPaint", "MOBS-EpyStrain_Flu"),
         model_id != "FluSight-ensemble") 
```


# Save to files

## Figure 1
```{r, fig.height =20, fig.width = 25}
(figure1a + figure1d) / (figure1c_model + figure1c_loc)
```
## Figure 5 (1.2, overflow)
```{r, fig.height = 20, fig.width = 20}
figure1b_loc + figure1b_date
```

## Figure 6
```{r, fig.height = 20, fig.width = 20}
fig1c_timeseries
```

## Saving
```{r}
png("Figures/figure1.png", width = 1920, height = 1920)
(figure1a + figure1d) / (figure1c_model + figure1c_loc)
dev.off()
```

```{r}
png("Figures/figure6.png", width = 1440, height = 1080)
fig1c_timeseries
dev.off()
```

```{r}
png("Figures/figure5.png", width = 1920, height = 1920)
(figure1b_loc + figure1b_date)
dev.off()
```

```{r}
png("Figures/figure7.png", width = 1575, height = 973)
(figure1b_date_line) # i just save it manually, it looks better
dev.off()
```

```{r}
png("Figures/figure8.png", width = 1575, height = 973)
(figure_50_split) # i just save it manually, it looks better
dev.off()
```

```{r}
png("Figures/figure9.png", width = 1575, height = 973)
(figure1d_split) # i just save it manually, it looks better
dev.off()
```