---
title: "Figure Generation"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, output_dir = "C:/Projects/ForecastEvaluation/HTML", encoding = encoding) })
urlcolor: blue
linkcolor: red
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6, fig.align = "left", warning=FALSE, echo=TRUE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

------------------------------------------------------------------------
```{r libraries, results='hide', warning=FALSE, message=FALSE, echo = FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(patchwork)
library(kableExtra)

library(scoringutils)
library(hubUtils)
library(hubEnsembles)
library(hubData)
```

# Data
```{r}
state_coverage <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_coverage.csv")
state_coverage_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_coverage_summary.csv")
state_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis.csv")
state_wis_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis_summary.csv")

standard_coverage <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_coverage.csv")
standard_coverage_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_coverage_summary.csv")
standard_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis.csv")
standard_wis_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis_summary.csv")
```

# Figure 1
Local versus state-level forecast performance
Fig.1 “Boilerplate” analysis comparing local vs state-level forecast performance, with relative WIS computed via treating the state forecast superimposed onto the local data as a baseline model
Using all models regardless of when they started submitting

## Relative WIS

# Figure 2
Model-based evaluation of aggregate versus local forecast performance
Fig. 2 Visual summary of model-based analysis, plotting intercept and model-specific effects + location specific effects
Using all models regardless of when they started submitting

# Figure 3
Model comparison across locations
Fig. 3 “Boilerplate” analysis comparing forecast performance by model for all locations and subset of models
Using the 6 models that submitted before the peak: (UT-GBQR, epiforecasts-dyngam, NAU-Copycat, UMass-alloy, NAU-INFLAenza, UMass-SAR, VTSanghani-Prime + epiengage-baseline + epiENGAGE-ensemble_mean)

# Figure 4
Model-based evaluation of model performance
Fig. 4 Visual summary of model-based analysis, plotting model-specific effects after accounting for epidemic phase, granularity of location, horizon, etc.
Using the 6 models that submitted before the peak: (UT-GBQR, epiforecasts-dyngam, NAU-Copycat, UMass-alloy, NAU-INFLAenza, UMass-SAR, VTSanghani-Prime + epiengage-baseline + epiENGAGE-ensemble_mean)