---
title: "Figure Generation"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, output_dir = "C:/Projects/ForecastEvaluation/HTML", encoding = encoding) })
urlcolor: blue
linkcolor: red
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6, fig.align = "left", warning=FALSE, echo=TRUE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

------------------------------------------------------------------------
```{r libraries, results='hide', warning=FALSE, message=FALSE, echo = FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(patchwork)
library(kableExtra)

library(scoringutils)
library(hubUtils)
library(hubEnsembles)
library(hubData)
```

# Data
```{r}
state_coverage <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_coverage.csv")
state_coverage_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_coverage_summary.csv")
state_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis.csv")
state_wis_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/state-scoring/state_wis_summary.csv")

standard_coverage <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_coverage.csv")
standard_coverage_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_coverage_summary.csv")
standard_wis <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis.csv")
standard_wis_summary <- read.csv("C:/Projects/ForecastEvaluation/Data/standard-scoring/standard_wis_summary.csv")
```

# Figure 1
Local versus state-level forecast performance
Fig.1 “Boilerplate” analysis comparing local vs state-level forecast performance, with relative WIS computed via treating the state forecast superimposed onto the local data as a baseline model
Using all models regardless of when they started submitting

## Relative WIS
In this case, the baseline model is the local model (regular application) with the state model being compared to the baseline. A higher rWIS score (>1) would mean the state model is worse. On the other hand, a smaller rWIS score (<1) means that the state model performed better than the baseline.
```{r}
state_wis = state_wis |> rename(state_wis = wis)
```

```{r}
complete_wis <- state_wis %>%
  left_join(standard_wis, by = intersect(colnames(state_wis), colnames(standard_wis)))

complete_wis$relative_wis <- complete_wis$state_wis / complete_wis$wis
complete_wis = complete_wis |> select("location", "target_end_date", "horizon", "reference_date",  "model_id", "target", "wis",  "state_wis",    "relative_wis")
```

```{r}
sum(is.na(complete_wis))
complete_wis = na.omit(complete_wis)
```

```{r}
complete_wis_summary <- complete_wis %>%
  group_by(model_id) %>%
  summarise(
    mean_relative_wis = mean(relative_wis),
    count = n(),
    .groups = 'drop'
  )

complete_wis_summary |> arrange(mean_relative_wis)

# complete_wis_summary_horizon <- complete_wis %>%
#   group_by(model_id, horizon) %>%
#   summarise(
#     mean_relative_wis = mean(relative_wis),
#     count = n(),
#     .groups = 'drop'
#   )
# 
# complete_wis_summary_horizon |> arrange(mean_relative_wis)
```

```{r}
ggplot(complete_wis_summary, aes(x = fct_reorder(model_id, mean_relative_wis, .desc = TRUE), y = mean_relative_wis)) +
  geom_col(fill = "firebrick", color = "black") +  coord_flip() +
  labs(x = "Model", y = "Mean Relative WIS (State / Baseline)") + theme_bw() 
```

# Figure 2
Model-based evaluation of aggregate versus local forecast performance
Fig. 2 Visual summary of model-based analysis, plotting intercept and model-specific effects + location specific effects
Using all models regardless of when they started submitting

# Figure 3
Model comparison across locations
Fig. 3 “Boilerplate” analysis comparing forecast performance by model for all locations and subset of models
Using the 6 models that submitted before the peak: (UT-GBQR, epiforecasts-dyngam, NAU-Copycat, UMass-alloy, NAU-INFLAenza, UMass-SAR, VTSanghani-Prime + epiengage-baseline + epiENGAGE-ensemble_mean)

# Figure 4
Model-based evaluation of model performance
Fig. 4 Visual summary of model-based analysis, plotting model-specific effects after accounting for epidemic phase, granularity of location, horizon, etc.
Using the 6 models that submitted before the peak: (UT-GBQR, epiforecasts-dyngam, NAU-Copycat, UMass-alloy, NAU-INFLAenza, UMass-SAR, VTSanghani-Prime + epiengage-baseline + epiENGAGE-ensemble_mean)