---
title: "Score Calculation"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
urlcolor: blue
linkcolor: red
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6, fig.align = "left", warning=FALSE, echo=TRUE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

------------------------------------------------------------------------
```{r libraries, results='hide', warning=FALSE, message=FALSE, echo = FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(patchwork)
library(kableExtra)

library(scoringutils)
library(hubUtils)
library(hubEnsembles)
library(hubData)
```

# Functions
```{r}
compute_wis_score <- function(df, predicted, observed, target_date) {
  df_wis <- df %>%
    rename(predicted = !!rlang::sym(predicted),
           observed = !!rlang::sym(observed),
           quantile_level = output_type_id) %>%
    dplyr::select(reference_date, location, horizon, target, target_end_date,
                  output_type, quantile_level, observed, predicted) |>
    as_forecast_quantile(
      forecast_unit = c("location", "target_end_date", "horizon", "target"),
      predicted = "predicted",
      quantile_col = "quantile_level"
    ) |>
    score() |>
    mutate(horizon = horizon + 1,
           reference_date = target_date) |>
    dplyr::select(location, target_end_date, horizon, reference_date, wis)
  return(df_wis)
}
```

# Data 
## Observed data
```{r}
# observed = read.csv("Data/oracle-output.csv") # the observed data does not have ILI ED Visits
```


## Model output
```{r}
# hub_path <- "C:/Projects/flu-metrocast"
# hub_con <- connect_hub(hub_path)
# predictions <- hub_con %>%
#   collect()
# 
# predictions <- predictions |> filter(location == tolower(location))
# write_csv(predictions, "Data/predictions.csv")
```

# Data processing
```{r}
# observed$target_end_date = as.Date(observed$target_end_date)
# df = left_join(predictions, observed, by = c("location", "target", "target_end_date"))
```

```{r}
# write_csv(df, "Data/raw_data.csv")
raw = read.csv("Data/raw_data.csv")
knitr::kable(head(raw))
```

# Standard scoring
## WIS calculation
```{r wis_calc, cache = TRUE}
# models <- unique(raw$model_id)
# dates <- sort(unique(raw$target_end_date))
# 
# results <- raw %>%
#   filter(!is.na(oracle_value)) %>%
#   {
#     models <- unique(.$model_id)
#     dates <- sort(unique(.$target_end_date))
# 
#     map_df(models, ~ {
#       model_name <- .x
# 
#       map_df(dates, ~ {
#         target_date <- .x
# 
#         raw_filtered <- raw %>%
#           filter(model_id == model_name,
#                  target_end_date == target_date,
#                  !is.na(oracle_value))
# 
#         if (nrow(raw_filtered) == 0) return(NULL)
# 
#         compute_wis_score(
#           df = raw_filtered,
#           predicted = "value",
#           observed = "oracle_value",
#           target_date = target_date
#         ) %>%
#           mutate(model_id = model_name,
#                  target = raw_filtered$target[1])
# 
#       })
#     })
#   }
```

```{r}
# write_csv(wis, "Data/standard-scoring/standard_wis.csv")

wis = read.csv("Data/standard-scoring/standard_wis.csv")
knitr::kable(head(wis))
```

```{r wis_summary}
# wis_summary <- results %>%
#   group_by(model_id, horizon, target) %>%
#   summarise(
#     mean_wis = mean(wis),
#     count = n(),
#     .groups = 'drop'
#   )
# 
# 
# write_csv(wis_summary, "Data/standard-scoring/standard_wis_summary.csv")

wis_summary = read.csv("Data/standard-scoring/standard_wis_summary.csv")
knitr::kable(head(wis_summary |> arrange(mean_wis)))
```

## Coverage rate
```{r coverage_calc}
# coverage <- raw %>%
#   filter(!is.na(oracle_value)) %>%
#   pivot_wider(
#     names_from = output_type_id,
#     values_from = value,
#     names_prefix = "quantile_"
#   ) %>%
#   mutate(
#     coverage_95 = as.numeric(oracle_value >= quantile_0.025 & oracle_value <= quantile_0.975)
#   ) %>%
#   select(model_id, location, target_end_date, horizon, target,
#          reference_date, output_type, oracle_value,
#          quantile_0.025, quantile_0.975, coverage_95)
# 
# 
# write_csv(coverage, "Data/standard-scoring/standard_coverage.csv")

coverage = read.csv("Data/standard-scoring/standard_coverage.csv")
knitr::kable(head(coverage))
```

```{r coverage_summary}
# coverage_summary <- coverage %>%
#   group_by(model_id, horizon, target) %>%
#   summarise(
#     coverage_rate = mean(coverage_95),
#     count = n(),
#     .groups = 'drop'
#   )
# 
# write_csv(coverage_summary, "Data/standard-scoring/standard_coverage_summary.csv")

coverage_summary = read.csv("Data/standard-scoring/standard_coverage_summary.csv")
knitr::kable(head(coverage_summary |> arrange(-coverage_rate)))
```

# State forecasts with local truth
## Lookup table
```{r}
# locations = read.csv("Data/locations.csv")
# lookup = locations |> select(location, state)
# lookup$state = tolower(lookup$state)
# 
# lookup <- lookup |>
#   mutate(state = case_when(
#     state == "north carolina" ~ "north-carolina",
#     state == "south carolina" ~ "south-carolina",
#     TRUE ~ state
#   ))
# 
# lookup <- lookup |> mutate(state = ifelse(location == state, "state", state))

# write_csv(lookup, "Data/lookup.csv")
lookup = read.csv("data/lookup.csv")
```

## Joins
```{r}
raw <- raw |> left_join(lookup, by = "location") # every row now has a state
sum(is.na(raw) == TRUE)
```

```{r}
# looks like these NA values are just the horizons not having data yet because it's too far in the future!
knitr::kable(head(raw |> filter(if_any(everything(), is.na))))
raw <- raw |> filter(!is.na(oracle_value))
sum(is.na(raw) == TRUE)
```

```{r}
# state data goes out and back in to merge
state_data <- raw |> 
  filter(state == "state") |> # state indicator
  select(reference_date, target, horizon, target_end_date, output_type, output_type_id, model_id, location, value) |> 
  rename(state_value = value, state = location)

raw <- raw |> left_join(state_data, by = c("reference_date", "target", "horizon", "target_end_date", "output_type", "output_type_id", "model_id", "state"))

raw = raw |> filter(location != "nyc") # removing new york
raw = raw |> filter(state != "state") # removing state
```

### NA value investigation
```{r}
sum(is.na(raw) == TRUE) 
na = raw |> filter(if_any(everything(), is.na)) |> filter(state != "state")
knitr::kable(table(na$state))
knitr::kable(table(na$target_end_date))
```

```{r}
na_sc = na |> filter(state == "south-carolina")
na_nc = na |> filter(state == "north-carolina")

knitr::kable(table(na_nc$model_id)) 
knitr::kable(table(na_sc$model_id))
```

I plan to remove the NAs for now until we can figure out what happened to these models in this timeframe, doesn't look systematic, maybe these ensemble models took a while to get online

```{r}
dim(raw)
raw = na.omit(raw)
dim(raw)
```

```{r}
# state_raw = raw |> select(-value)
# write_csv(state_raw, "Data/state_raw.csv")

state_raw = read.csv("Data/state_raw.csv")
sum(is.na(state_raw) == TRUE)
```
## WIS calculation
```{r}
# models <- unique(state_raw$model_id)
# dates <- sort(unique(state_raw$target_end_date))
# 
# state_results <- state_raw %>%
#   filter(!is.na(state_value)) %>%
#   {
#     models <- unique(.$model_id)
#     dates <- sort(unique(.$target_end_date))
# 
#     map_df(models, ~ {
#       model_name <- .x
# 
#       map_df(dates, ~ {
#         target_date <- .x
# 
#         state_raw_filtered <- state_raw %>%
#           filter(model_id == model_name,
#                  target_end_date == target_date,
#                  !is.na(state_value))
# 
#         if (nrow(state_raw_filtered) == 0) return(NULL)
# 
#         compute_wis_score(
#           df = state_raw_filtered,
#           predicted = "state_value",
#           observed = "oracle_value",
#           target_date = target_date
#         ) %>%
#           mutate(model_id = model_name,
#                  target = state_raw_filtered$target[1])
# 
#       })
#     })
#   }
```

```{r}
# write_csv(state_results, "Data/state-scoring/state_wis.csv")

state_wis = read.csv("Data/state-scoring/state_wis.csv")
knitr::kable(head(state_wis))
```

```{r}
# state_wis_summary <- state_wis %>%
#   group_by(model_id, horizon, target) %>%
#   summarise(
#     mean_wis = mean(wis),
#     count = n(),
#     .groups = 'drop'
#   )
# 
# write_csv(state_wis_summary, "Data/state-scoring/state_wis_summary.csv")

state_wis_summary = read.csv("Data/state-scoring/state_wis_summary.csv")
knitr::kable(head(state_wis_summary |> arrange(mean_wis)))
```

## Coverage rate
```{r}
# state_coverage <- state_raw %>%
#   filter(!is.na(state_value)) %>%
#   pivot_wider(
#     names_from = output_type_id,
#     values_from = state_value,
#     names_prefix = "quantile_"
#   ) %>%
#   mutate(
#     coverage_95 = as.numeric(oracle_value >= quantile_0.025 & oracle_value <= quantile_0.975)
#   ) %>%
#   select(model_id, location, target_end_date, horizon, target,
#          reference_date, output_type, oracle_value,
#          quantile_0.025, quantile_0.975, coverage_95)
```

```{r}
# write_csv(state_coverage, "Data/state-scoring/state_coverage.csv")

state_coverage = read.csv("Data/state-scoring/state_coverage.csv")
knitr::kable(head(state_coverage))
```

```{r}
# state_coverage_summary <- state_coverage %>%
#   group_by(model_id, horizon, target) %>%
#   summarise(
#     coverage_rate = mean(coverage_95),
#     count = n(),
#     .groups = 'drop'
#   )
# 
# write_csv(state_coverage_summary, "Data/state-scoring/state_coverage_summary.csv")

state_coverage_summary = read.csv("Data/state-scoring/state_coverage_summary.csv")
knitr::kable(head(state_coverage_summary |> arrange(-coverage_rate)))
```
